A Horrocks-type theorem for even orthogonal $K_2$

### 2020-04-01 dl-paper.tex
Minor

It is easy to check that $\widetilde{P}_{\alpha, M}(0)$ contains the image of $Z_\alpha(A, M)$ under the natural embedding of $\overline{\St}(\Phi, A, M) \hookrightarrow \overline{\St}(\Phi, A[X], M[X])$.
In particular, if $M$ is the maximal ideal of $A$, the subgroup $\widetilde{P}_{\alpha, M}(0)$ contains relative Dennis--Stein and Steinberg symbols. It is also easy to see that, in fact, the image of $\widetilde{P}_{\alpha, M}(0)$ under the homomorphism $ev_{X=0}^*$ coincides with $Z_\alpha(A, M)$. \end{rem}

@@

In the sequel we often use the following property of $S_\alpha(a, -)$.
\begin{lemma} \label{lem:Smult}
For $g_1 \in P_\alpha(m)$, $g_2 \in P_\alpha(*)$ one has
$S_\alpha(a, g_1\cdot g_2) = S_\alpha(a, g_1) \cdot S_\alpha\left(\tfrac{a}{1+am}, g_2\right).$
\end{lemma} \begin{proof} Assume $g_2\in P_\alpha(m')$ for some $m' \in M$, so that $g_1 \cdot g_2 \in P_\alpha(m + m')$. The assertion now follows from the definition of $S_\alpha(a, -)$ and the centrality of Steinberg symbols:
\begin{multline*} S_\alpha(a, g_1 \cdot g_2) = x_\alpha(aX^{-1}) \cdot g_1 \cdot g_2 \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1+am+am'}\right) \cdot \{X, 1 + am + am'\} = \\ = x_\alpha(aX^{-1}) g_1  x_\alpha\left(-\tfrac{aX^{-1}}{1+am}\right) \cdot x_\alpha\left(\tfrac{aX^{-1}}{1+am}\right) g_2 x_\alpha\left(-\frac{\tfrac{a}{1+am}\cdot X^{-1}}{1 + \tfrac{a}{1+am}\cdot m'}\right) \cdot \{X, (1+am)\left(1 + \tfrac{am'}{1+am}\right)\} = \\ = S_\alpha(a, g_1) \cdot S_\alpha\left(\tfrac{a}{1+am}, g_2\right). \qedhere \end{multline*}
\end{proof}
It is clear that the restriction of the map $S_\alpha(a, g)$ to the subgroup $P_\alpha(0)$ coincides with the homomorphism of left conjugation by $x_\alpha(aX^{-1})$.
\begin{lemma}\label{P0_conj} The subgroup $P_\alpha(0)$ is stable under conjugation by $x_\alpha(aX^{-1})$ for arbitrary $a\in A$. \end{lemma}
\begin{proof} 
Since $P_\alpha(0)$ has the same generators as $\widetilde{P}_{\alpha, M}(0)$ we need to verify that the conjugate by $x_\alpha(aX^{-1})$ to every generator from~\cref{defP0} lies in $P_\alpha(0)$. 
The assertion is clear for the generators of type 3 and 5.

>>>>

It is easy to check that $\widetilde{P}_{\alpha, M}(0)$ contains the image of $Z_\alpha(A, M)$ under the natural embedding of $\overline{\St}(\Phi, A, M) \hookrightarrow \overline{\St}(\Phi, A[X], M[X])$.
In particular, if $M$ is the maximal ideal of $A$, the subgroup $\widetilde{P}_{\alpha, M}(0)$ contains relative Dennis--Stein and Steinberg symbols. It is also easy to see that the image of $\widetilde{P}_{\alpha, M}(0)$ under the homomorphism $ev_{X=0}^*$ coincides with $Z_\alpha(A, M)$. \end{rem}

@@

In the sequel we often use the following property of $S_\alpha(a, -)$.
\begin{lemma} \label{lem:Smult}
For $g_1 \in P_\alpha(m)$, $g_2 \in P_\alpha(*)$ one has
$S_\alpha(a, g_1\cdot g_2) = S_\alpha(a, g_1) \cdot S_\alpha\left(\tfrac{a}{1+am}, g_2\right).$
\end{lemma} \begin{proof} Assume $g_2\in P_\alpha(m')$ for some $m' \in M$, so that $g_1 \cdot g_2 \in P_\alpha(m + m')$. The assertion now follows from the definition of $S_\alpha(a, -)$ and~\eqref{eq:symbol-properties}:
\begin{multline*} S_\alpha(a, g_1 \cdot g_2) = x_\alpha(aX^{-1}) \cdot g_1 \cdot g_2 \cdot x_\alpha\left(-\tfrac{aX^{-1}}{1+am+am'}\right) \cdot \{X, 1 + am + am'\} = \\ = x_\alpha(aX^{-1}) g_1  x_\alpha\left(-\tfrac{aX^{-1}}{1+am}\right) \cdot x_\alpha\left(\tfrac{aX^{-1}}{1+am}\right) g_2 x_\alpha\left(-\frac{\tfrac{a}{1+am}\cdot X^{-1}}{1 + \tfrac{a}{1+am}\cdot m'}\right) \cdot \{X, (1+am)\left(1 + \tfrac{am'}{1+am}\right)\} = \\ = S_\alpha(a, g_1) \cdot S_\alpha\left(\tfrac{a}{1+am}, g_2\right). \qedhere \end{multline*}
\end{proof}
It is clear that the restriction of the map $S_\alpha(a, g)$ to the subgroup $P_\alpha(0)$ coincides with the homomorphism of left conjugation by $x_\alpha(aX^{-1})$.
\begin{lemma}\label{P0_conj} The subgroup $P_\alpha(0)$ is stable under conjugation by $x_\alpha(aX^{-1})$ for arbitrary $a\in A$. \end{lemma}
\begin{proof} 
Since $P_\alpha(0)$ has the same generators as $\widetilde{P}_{\alpha, M}(0)$ we need to verify that the conjugate by $x_\alpha(aX^{-1})$ to every generator from~\cref{defP0} lies in $P_\alpha(0)$. 
The assertion is clear for the generators of type 3 and 5.
